\thetitle

### 2021-03-03 writing/challenges.tex
blame sequences becomes blame sets

The {\em first challenge\/} stems from the differences between the blame
assignment mechanisms of the three semantic variants.  While Natural assigns
blame to {\em one\/} component, Transient assigns blame to a sequence of
components. The Erasure semantics does not blame components {\it per se\/}, but
it comes with an exception location and a stack trace, which implicitly suggests
parties to blame.  Each strategy affects the behavior of the rational programmer
differently (and real ones, too).

One way to reconcile these differences is to {\em equip the rational
programmer with modes \/} that represent the different types of
information the rational programmer takes into account when debugging a
scenario. Intuitively, with the common vocabulary of modes, different
blame strategies become different ways the rational programmer  interprets
blame.  For instance, one Transient mode may pick the oldest element of a
blame set as the next component to add types because it corresponds to the
earliest point in the program's evaluation that can discover an impedance
mismatch.  Another mode may opt to treat the sequence as a stack and add
types to its newest element.  If both modes are equally successful in
locating an impedance mismatch, measuring the rational programmer's effort with each mode
may answer which is the most effective.

>>>>

The {\em first challenge\/} stems from the differences between the blame
assignment mechanisms of the three semantic variants.  While Natural assigns
blame to {\em one\/} component, Transient assigns blame to a set of
components. The Erasure semantics does not blame components {\it per se\/}, but
it comes with an exception location and a stack trace, which implicitly suggests
parties to blame.  Each strategy affects the behavior of the rational programmer
differently (and real ones, too).

One way to reconcile these differences is to {\em equip the rational
programmer with modes \/} that represent the different types of
information the rational programmer takes into account when debugging a
scenario. Intuitively, with the common vocabulary of modes, different
blame strategies become different ways the rational programmer  interprets
blame.  For instance, one Transient mode may pick the oldest element of a
blame set as the next component to add types because it corresponds to the
earliest point in the program's evaluation that can discover an impedance
mismatch.  Another mode may opt to treat the set as a stack and add
types to its newest element.  If both modes are equally successful in
locating an impedance mismatch, measuring the rational programmer's effort with each mode
may answer which is the most effective.

### 2021-03-03 writing/discussion.tex
blame sequences becomes blame sets

The results in section~\ref{sec:results} show that Transient produces empty
blame sequences for 967 scenarios. In theory, empty sequence must not occur. An
empty blame sequence means a lack of boundary crossings for the witness value.
By implication, a typed module is blaming itself---something that can
happen only if the type checker (or system) is unsound.

>>>>

The results in section~\ref{sec:results} show that Transient produces empty
blame sets for 967 scenarios. In theory, empty set must not occur. An
empty blame set means a lack of boundary crossings for the witness value.
By implication, a typed module is blaming itself---something that can
happen only if the type checker (or system) is unsound.

### 2021-03-03 writing/results.tex
results: bring back wrapfigure for success rates
blame sequences becomes blame sets

\begin{figure}
  \includegraphics[width=0.40\textwidth]{./plots/success-bars}

  \vspace{1em}
  \begin{minipage}{0.95\textwidth}
  The estimated percentage of scenarios for which each mode succeeds in locating the bug.
  The upper bound margin of error is 0.02\%.
  \end{minipage}

  \caption{Success rates.}
  \label{fig:success-bars}
\end{figure}

@@

In Transient, similar to Natural, most failures are due to unhelpful
exception information (1851 for both Transient first and last blame).
However, Transient also has a substantial number of failures because
scenarios hit the time and memory limits of our experiment
(\textasciitilde770 scenarios).  Additionally, there are nearly 1,000
cases where Transient reports an empty blame set, leaving the rational
programmer without hints about how to proceed.
Sections~\label{sec:threat:transient} and ~\label{sec:threat:transient2}
explain how both of these causes of failure for Transient affect our
experiment.

>>>>

\begin{wrapfigure}{r}{.40\textwidth}
  \includegraphics[width=0.40\textwidth]{./plots/success-bars}

  \vspace{1em}
  \begin{minipage}{0.4\textwidth}
  The estimated percentage of scenarios for which each mode succeeds in locating the bug.
  The upper bound margin of error is 0.02\%.
  \end{minipage}

  \caption{Success rates.}
  \label{fig:success-bars}
\end{wrapfigure}

@@

In Transient, similar to Natural, most failures are due to unhelpful
exception information (1851 for both Transient first and last blame).
However, Transient also has a substantial number of failures because
scenarios hit the time and memory limits of our experiment
(\textasciitilde770 scenarios).  Additionally, there are nearly 1,000
cases where Transient reports an empty blame set, leaving the rational
programmer without hints about how to proceed.
Sections~\ref{sec:threat:transient} and ~\ref{sec:threat:transient2}
explain how both of these causes of failure for Transient affect our
experiment.
